Differentially Private Bayesian Inference

### 2018-07-08 main-workshop.tex
update submission version

\section{Bayesian Inference Based on Dirichlet-Bernoulli Distribution}
\label{sec_bayesInfer}
In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$. Then, we get some observed data $x$ sizing $n$, and produce a posterior distribution $Pr(\xis | x)$. The Bayesian inference is based on the Bayes' rule to calculate the posterior distribution:
\begin{equation*}
Pr(\xis | x) = \frac{Pr(x | \xis) \pi(\xis)}{Pr(x)}
\end{equation*}
It is denoted as $\bysinfer(x,\pi(\xis))$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

@@

\section{Algorithm Setting up}
\label{sec_setup}
For now, we already have a prior distribution $\pi(\xis)$, an observed data set $x$.

\subsection{Exponential Mechanism with Global Sensitivity}
\label{subsec_emgs}

% \subsubsection{Mechanism Set up}

In exponential mechanism, candidate set $\mathcal{R}$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
\mathcal{R} = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}

Hellinger distance $\hlg$ is used here to score these candidates. The utility function:
\begin{equation}
\label{equ_utility}
u(x,r) = -\hlg(\bysinfer(x), r); r \in \mathcal{R}.
\end{equation}

Exponential mechanism with global sensitivity selects and outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
\end{equation*}
where global sensitivity is calculated by:
\begin{equation*}
\Delta_{g}u = 
\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|
\end{equation*}

The basic exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.

% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$. Since $\hlg$ is monotonic, i.e. our utility function is monotonic.

% \subsubsection{Security Analysis}
% It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\bysinfer$ with privacy mechanism as $\privinfer$. For adjacent data set $||x,y||_1 = 1$:
% \begin{equation*}
% \begin{split}
% \frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
% & =\frac
% {\frac
% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
% {\frac
% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
% & = \left(\frac
% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
% \right)
% \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & = exp\left(\frac
% {\epsilon (u(x,r) - u(y,r))}
% {2 \Delta_{g}u}
% \right)
% \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & \leq
% exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & = exp(\epsilon).
% \end{split}
% \end{equation*}

% Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.

\subsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
\end{equation*}

where local sensitivity is calculated by:

\begin{equation*}
\Delta_{l}u(x) = 
\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}.
\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|
\end{equation*}

The exponential mechanism with local sensitivity is non differential privacy\cite{dwork2014algorithmic}.

\subsection{Exponential Mechanism with Smooth Sensitivity}
\label{sec_smoo}

@@

\section{Accuracy Analysis}
\subsection{Laplace Mechanism}
\label{subsec_accuracy_lap}
Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{2}}.
\end{equation*}

So we have the probability $Pr[| Lap_i |] = Pr[| Lap_i | \leq |Y| < | Lap_i | + 1] = e^{- \frac{| Lap_i | \epsilon}{2}} - e^{- \frac{(| Lap_i | + 1) \epsilon}{2}}$.

When we are in the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d. Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output. Then the probability of each group of noises are calculated as $Pr[\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}] = Pr[| Lap_1 | \leq |Y| < | Lap_1 | + 1] \times Pr[| Lap_2 | \leq |Y| < | Lap_2 | + 1] \times \cdots \times Pr[| Lap_{m-1} | \leq |Y| < | Lap_{m-1} | + 1] = (e^{- \frac{| Lap_1 | \epsilon}{2}} - e^{- \frac{(| Lap_1 | + 1) \epsilon}{2}}) \times (e^{- \frac{| Lap_2 | \epsilon}{2}} - e^{- \frac{(| Lap_2 | + 1) \epsilon}{2}}) \times \cdots \times (e^{- \frac{| Lap_{m-1} | \epsilon}{2}} - e^{- \frac{(| Lap_{m-1} | + 1) \epsilon}{2}})$.

% where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
% \begin{equation*}
% \begin{split}
% Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
% & = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
% & = \gamma
% \end{split} 
% \end{equation*}

\subsection{Exponential Mechanism with Global Sensitivity}
\label{subsec_accuracy_global}
Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
\end{equation*}
where $|R|$ is the size of the candidate set. Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$

\subsection{Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_smoo}
We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.

First is the tight bound with very accurate calculation.
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] = \sum\limits_{\{z | \hlg(\bysinfer(x), z) \geq c\}} \frac{e^{\frac{- \epsilon \hlg(\bysinfer(x), z)}{S(x)}}}{NL_x}.
\end{equation*}

In order to be more efficient, we designed the second accuracy bound which is slightly looser than the first one:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{NL_x}.
\end{equation*}

In the second bound, we still need to calculate the normaliser every time. So we want make further improvements on efficiency like follows:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
\end{equation*}
where we replace the $NL_x$ with a value only related to the size of the data. However, we haven't figured out the formula of this $N(n)$.

Within the three accuracy bounds, we will mainly use the first one in following analysis.

\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_tradeoff}
Based on accuracy study above, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism in four aspects: data size, dimensions, prior distribution and data variance.

\subsubsection{Accuracy Analysis wrt. Data Size and Distribution Dimensions}
In this part, we will analyze the influence of data size on the two mechanisms' discrete probabilities of outputting each candidate separately. In following analysis, we will count the probabilities wrt. the steps from correct answer, in order to be more concise. For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$. Under the Hellinger distance measurement, if candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer. i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$. This will make the results more clear and observable.

\begin{itemize}

	\item In our exponential mechanism, the probability of outputting candidates wrt. steps (i.e., the hellinger distance) from the correct answer is calculated as:

	\begin{equation*}
	\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) = c] = \sum\limits_{\{z| \hlg(\bysinfer(x), z) = c\}}\frac{exp(\frac{- \epsilon c}{S(x)})}
	{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
	\end{equation*}

	Each candidate will occupy a portion of ``$1$'' as their outputting probability. Supposing candidates within three steps from the correct answer are good answers, the portion occupied by the good answers is decreasing when the size of candidate set increasing. That's to say, the probabilities of outputting good answers are decreasing when the data size and dimension of prior distribution increasing. More specifically, the candidate set size is $\sim n^{m-1}$, which means the probabilities of outputting good answers are decreasing with speed $\sim n^{m-1}$.

	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set. In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are i.i.d. So, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:

	\begin{equation*}
	\begin{split}
	Pr[(Lap_1, Lap_2, \cdots, Lap_{m-1})]  
	& = Pr[Lap_1 \leq Lap(\frac{2}{\epsilon}) < Lap_1 + 1] \\
	& \times Pr[Lap_2 \leq Lap(\frac{2}{\epsilon}) < Lap_2 + 1] \times \cdots \\
	& \times Pr[Lap_{m-1} \leq Lap(\frac{2}{\epsilon}) < Lap_{m-1} + 1],
	\end{split}
	\end{equation*}
	where $Pr[Lap_i \leq Lap(\frac{2}{\epsilon}) < Lap_i + 1] = \frac{1}{2} Pr[|Lap_i| \leq Lap(\frac{2}{\epsilon}) < |Lap_i| + 1]$ when $Lap_i > 0$ and $\frac{1}{2} Pr[|Lap_i| - 1 \leq Lap(\frac{2}{\epsilon}) < |Lap_i|]$ else.

	From analysis above, we can see the probabilities of outputting the good answers will not change a lot as the size of the candidate set increasing. Specifically, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by , which means the probability of correct answer will decrease very little no matter how large the candidate set is.

	\item Then, we do some concrete cases analysis.

	\begin{itemize}

		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are:

		\begin{center}
		 \begin{tabular}{c | c | c} 
		 \hline
		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		 \hline\hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.83737258593] / 4		$ & 0.0431193490585 & 0.066561234758\\ 
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.662174391701 ] / 3	$ & 0.0785621424847 & 0.0992976939175  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.457635865026 ] / 2	$ & 0.158265808563 & 0.148134752205  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.233629480709 ] / 1	$ & 0.340809715054 & 0.220991081918  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 				$ & 0.37924298484 & 0.329679953964 \\
		 \hline
		\end{tabular}
		\end{center}

		Here, there are only 5 kinds of steps from correct answer. Our mechanism in the second column is clearly better than Laplace mechanism in the third column. When the candidates are close to correct answer (for example, $0, 1, 2$ steps from correct answer), our mechanism can output them with higher probabilities than Laplace mechanism. On the other hand, when candidates are far away from correct answer (for example, $3, 4$ steps), our mechanism can output them with lower probabilities.

		\item keep the prior unchanged, $\betad(1,1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$

		\begin{center}
		 \begin{tabular}{c | c | c} 
		 \hline
		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		 \hline\hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.999999984481] / \cdots 	$ & 0.000149705644585 & 3.05988187701e-09\\ 
		 \hline
		 \multicolumn{3}{c}{$\cdots$}  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.187421762881] / 2		$ & 0.0548161224677 & 0.0285774941516 \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.110122822057 ] / 1		$ & 0.192227323562 & 0.170131188571  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.0713016293602 & 0.108688872046 \\
		 \hline
		\end{tabular}
		\end{center}

		This case shows that the Laplace mechanism do much better than our exponential mechanism significantly. These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism. Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.

		% In this case, it is hard to tell which one is better because Laplace mechanism can output some good answers (for example, the correct answer) better than our mechanism but cannot go better with other good answers.

		% \item when the prior is $\dirichlet(1,1,1,1)$, the observed data set is $(1,1,1,50)$ (the same meaning as above), we can get the posterior distribution $\dirichlet(2,2,2,51)$. Some probabilities from the two mechanisms are listed as follows:
		% \begin{center}
		%  \begin{tabular}{c | c | c} 
		%  \hline
		%  Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		%  \hline\hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.999999999998] / \cdots 	$ & 0.000213865923868 & 6.16388940464e-11\\ 
		%  \hline
		%  \multicolumn{3}{c}{$\cdots$}  \\
		%  \hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.340503311163] / 2		$ & 0.000388935212208 & 0.0360289071389 \\
		%  \hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.249722620018 ] / 1		$ & 0.000464587461035 & 0.0360289071389  \\
		%  \hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.000252512987228 & 0.0358325423325 \\
		%  \hline
		% \end{tabular}
		% \end{center}

		% This case shows that the Laplace mechanism do much better than our exponential mechanism significantly. These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism. Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.

\subsubsection{Accuracy Analysis wrt. prior distribution}
In this part, we firstly study the local sensitivity of Hellinger distance of different $\betad$ distributions as in Fig. \ref{fig_sensitivity}, in order to have a better understanding of the relationships between accuracy and next two aspects.

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{sensitivity}
\label{fig_sensitivity}
\caption{Hellinger distance study}
\end{figure}

As in Fig. \ref{fig_sensitivity}, the local sensitivity of Hellinger distance will decrease when $\betad$ distribution's two parameters get closer (i.e. more uniform) and larger. In the same time, our smooth sensitivity will also decrease based on the Def. \ref{def_smoo}. From accuracy bound in Sec. \ref{subsec_accuracy_smoo}, the accuracy will be improved when sensitivity go larger. In consequence, when we increase the prior distribution, the smooth sensitivity in our exponential mechanism will decrease, which means our accuracy will be improved. However, the sensitivity of $l_1$ norm in Laplace mechanism is fixed regardless the prior distribution. We will study this trade-off in Sec. \ref{subsubsec_vs_prior}.

\subsubsection{Accuracy Analysis wrt. data variance}

Similar as above, when the data variance is small (i.e. the data are uniform), the parameters of posterior distribution will get more uniform (i.e. closer). Based on Fig. \ref{fig_sensitivity}, the Hellinger distance's sensitivity will get smaller when parameter get closer. As a result, the accuracy will be improved in the same time. We will study this trade-off in Sec. \ref{subsubsec_vs_variance}

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{efficiency}
\label{fig_efficiency}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\end{figure}

\section{Experimental Evaluations}
\label{sec_experiment}

@@

In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
\begin{enumerate}
	\item Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity. Both of the two exponential mechanisms are do much better than it with global sensitivity.
	\item The accuracy of our exponential mechanism is better than Laplace mechanism. But the advantages are not significant.
\end{enumerate}

@@

% \subsubsection{Experiment Analysis}
% In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism. By computing the two mechanisms' discrete probabilities wrt. steps (i.e., Hellinegr distance) from correct answer under different settings, we got groups of results as in Fig. \ref{fig_theory_50_50}, \ref{fig_theory_20_20_20}, \ref{fig_theory_20_20_20_20} and \ref{fig_theory_1_1_1_77}.

% Subfigs (a) based on Sec. \ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times. The x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance. Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt. the steps. The x-axis is the Hellinger distance from correct answer, i.e. steps from correct answer. Since they have the same meaning, we just use the Hellinger distance to label the x-axis here. The y-axis is the probability of output candidates with corresponding steps (i.e. Hellinger distance) from correct answer.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{50_50.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_50_50}
% \end{center}
% \end{figure*}

% When the data size and the dimension of the prior distribution is small, our exponential mechanism can do better than Laplace, both in experiments and in theory, as shown in Fig. \ref{fig_theory_50_50}. In Subfig. \ref{fig_theory_50_50}(a), the experiment results show that the average Hellinger distance of our mechanism's outputs are smaller than Laplace mechanism, i.e., the average accuracy of our mechanism is higher than Laplace mechanism. In the mean time, the theory calculation results in Subfig. \ref{fig_theory_50_50}(b) also show that our exponential mechanism can output good answers with higher probabilities and output bad answers with lower probabilities than Laplace mechanism.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20)$, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_20_20_20}
% \end{center}
% \end{figure*}

% In Fig. \ref{fig_theory_20_20_20}, we plotted the results under the case ($x = (20,20,20)$). SubFig. \ref{fig_theory_20_20_20}(a) shows that the average accuracy of Laplace mechanism is slightly better than our mechanism. Meanwhile, the SubFig. \ref{fig_theory_20_20_20}(b) shows the Laplace mechanism have higher probabilities on some good answers but lower on some other good answers. The advantage is not significant. So, we increase the data size and the dimension in next case to have a further study.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_20_20_20_20}
% \end{center}
% \end{figure*}

% Here we studied the case when data size $n = 80$ and observed data set $x=(20,20,20,20)$ and plotted these discrete probabilities, shown in Fig. \ref{fig_theory_20_20_20_20}.  Subfig. \ref{fig_theory_20_20_20_20}(a) shows that the Laplace mechanism is better than our exponential mechanism very obviously. Subfig \ref{fig_theory_20_20_20_20}(b) shows that the Laplace can output most of the good answers with higher probabilities than our exponential mechanism. The advantage in the SubFig. \ref{fig_theory_20_20_20_20}(a) is obvious but still not significant in SubFig. \ref{fig_theory_20_20_20_20}(b). So, we change the variance of the observed data set in the next case.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_1_1_1_77}
% \end{center}
% \end{figure*}

% In Fig. \ref{fig_theory_1_1_1_77}, we considered an edge case where the variance of the observed data set is small: $x=(1,1,1,77)$ and plotted these discrete probabilities. This plot can show clearly that the Laplace mechanism is much better than our exponential mechanism, both in (a) and (b). In Subfig. \ref{fig_theory_1_1_1_77}(b), the average accuracy of Laplace mechanism is conspicuously better than the other three exponential mechanisms. Also, in Subfig. \ref{fig_theory_1_1_1_77}(b), the Laplace mechanism can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously. Moreover, no matter good answers or bad answers, their outputting probabilities are very close in our exponential mechanism.

% From the theory and experimental analysis above, we obtained some conclusions
% \begin{enumerate}
% 	\item when the data size and the dimensions of the prior distribution are small (candidate set size $n^{m-1}$ around 5000, our exponential mechanism with smooth sensitivity can do better than Laplace mechanism.

% 	\item when the observed data set is close to center (i.e., the variance is large), the performance of the two mechanisms are close to each other.

% 	\item The Laplace mechanism will beat us when the data size and the dimensions of the prior distribution increasing and when the variance of the observed data set is small.
% \end{enumerate}

\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
\label{subsec_vs_variables}

In this section, we evaluate the accuracy wrt. four variables, including data size, dimension, data variance and prior distribution, and some combinations of these variables. We experiment 1000 times under each value of variables and produce 4-quantile plots for each variable. In following 4-quantile plots, the y-axis is accuracy measured by Hellinger distance, x-axis is different value of variables. The blue boxes in plots represent our exponential mechanism and the next yellow box represents the Laplace mechanism under the same setting.

\subsubsection{Accuracy Evaluation wrt. Datasize}
\label{subsubsec_vs_datasize}

\begin{figure*}
\begin{center}
\centering
  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1.eps}}
  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$}
\label{fig_vs_datasize}
\end{center}
\end{figure*}

In Fig. \ref{fig_vs_datasize}, both of the two plots show that when data size go larger, accuracy of our exponential mechanism are decreasing. In Fig. \ref{fig_vs_datasize}(a), when the data size is smaller than 12, we can beta Laplace mechanism but fail when data size larger than or equal to 12. Same as in Fig. \ref{fig_vs_datasize}(b), we can beat Laplace mechanism when data size is smaller than 15 and fail otherwise.

\subsubsection{Accuracy Evaluation wrt. Dimensions}
\label{subsubsec_vs_dimension}

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{accuracy_vs_dimension}
\caption{Accuracy measurement based on Hellinger distance wrt. different dimensions and data size. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_dimension}
\end{figure}

In Fig. \ref{fig_vs_dimension}, x-axis are observed data sets of different size and dimensions. The plot shows that dimensions have similar influence on our exponential mechanism and the Laplace mechanism. Accuracy of two mechanisms both decrease when dimensions go larger. We will be beat by Laplace mechanism when data size increase but will not be affected when dimensions increase. In other words, dimension has little influence on whether we will beat Laplace mechanism.

\subsubsection{Accuracy Evaluation wrt. Data variance}
\label{subsubsec_vs_variance}

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{accuracy_vs_mean_1_1}
\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_variance}
\end{figure}

In Fig. \ref{fig_vs_variance}, x-axis are observed data sets of different variances (or means). We study this variable under two-dimension $\betad$ distribution in order to be concise. It shows that our mechanism's accuracy is better when data variance go smaller, meanwhile Laplace mechanism go worse. We will beat Laplace mechanism when observed data are more uniformly.

\subsubsection{Accuracy Evaluation wrt. Prior Distribution}
\label{subsubsec_vs_prior}

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{accuracy_vs_prior_5_5_5}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
\label{fig_vs_prior}
\end{figure}

In Fig. \ref{fig_vs_prior}, we study this variable under setting that observed data set is $[5,5,5]$ because in Fig. \ref{fig_vs_datasize} Laplace mechanism beat us when data size is 15 and uniformly distributed. The plot shows that in the beginning we cannot beat Laplace but when prior distribution grow larger, we perform better and better and beat Laplace mechanism finally.

\subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
\label{subsubsec_vs_prior_variance}

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\label{fig_vs_prior_variance}
\end{figure}

Here, we change the prior distribution and data variance in the same time. As shown in Fig. \ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary. Moreover, our mechanism is improving continuously and significantly as prior distribution increasing while Laplace mechanism isn't.

>>>>

\section{Problem Statement}

\section{Technical Problem Statement}
\label{sec_bayesInfer}

Our technical problem is based on the Bernoulli-Beta Bayesian inference. In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$. Then, we get some observed data $x$ sizing $n$, and produce a posterior distribution $Pr(\xis | x)$. The Bayesian inference is based on the Bayes' rule to calculate the posterior distribution:
\begin{equation*}
Pr(\xis | x) = \frac{Pr(x | \xis) \pi(\xis)}{Pr(x)}
\end{equation*}
It is denoted as $\bysinfer(x,\pi(\xis))$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

@@

\section{Baseline Approach}

\section{Our Approach - Exponential Mechanism with Smooth Sensitivity}
\label{sec_smoo}

@@

\section{Preliminary Experimental Results}
\label{sec_experiment}

@@

In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close.

\section{Conclusions}
We can obtain some preliminary conclusions: 
\begin{enumerate}
	\item Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity. Both of the two exponential mechanisms are do much better than it with global sensitivity.
	\item The accuracy of our exponential mechanism is better than Laplace mechanism. But the advantages are not significant.
\end{enumerate}

@@
